Designing Turk Experiments for Visual Statistical Inference

### 2013-06-20 paper_turk.tex
sample size updates

To make sure that the observed data set truly represents the Model \eqref{eqn:turk_model} we suggest three approaches. One is Kolomogorov test statistic approach and the other two approaches are quantiles of $p$-values and closeness of estimated parameters to the true parameters. To illustrate the three approaches we used Model \eqref{eqn:turk_model} as an example but the idea can be extended to any situation. The three approaches are discussed below. \\

{\bf Kolomogorov test statistic approach:} In this approach we simulate 1000 data sets from Model \eqref{eqn:turk_model}  and obtain Kolmogorov test statistic for each set of data as below. $$D_n=\sup_x |F_n(x)-F(x)|$$ where $F_n(x)=\frac1n \sum_{i=1}^n I_{X_i\le x}$ be the empirical distribution function of fitted residuals, $I_{X_i\le x}$ be the indicator function equal to 1 if $X_i\le x$ and equal to 0 otherwise and $F(x)$ be the cumulative function of normal with mean zero(0) and variance $\sigma^2$. We keep the data set that has minimum value for Kolmogorov test statistic since for this data set $F_n(x)$ should be the closest to the desired normal model.  \\

@@

{\bf Closeness of estimated parameters:} When we simulate a data set from the Model \eqref{eqn:turk_model} and fit the model to the data set again, we do not get the parameters estimates same as what we fixed while simulation. For example, we obtained a parameter estimates of 0.5 for true $\beta=3$. We want a data set where the parameter is closed to our fixed slope $\beta=3$.  In this approach we generate 1000 data sets and pick the data set that shows most close estimates of parameters compared to true parameter values.

@@

\subsection{Sample size estimation} By sample size we mean the number of evaluations per lineup. It is different than number of people who evaluates lineup. If multiple lineups are evaluated by a person, sample size will be larger than number of people recruited from MTurk.

To have an idea how many evaluations are required for a lineup one approach can be to have a prior idea of proportion correct for the lineup. For a given proportion $p$ we want to have margin of error (ME) to be 0.1. Thus we have $$ME =1.96 \sqrt{ \frac 1 n p(1-p)} \le 0.05$$ which gives us the estimation of minimum sample size $$n \geq \frac{p(1-p)}{(0.05/1.96)^2}.$$

If we do not have any prior idea of proportion of correct or power, we need to rely on the power of similar conventional test. This can be assumed to be the power or proportion correct for that lineup. Other ways of having an estimate of sample size can be very specific to the problem of interest and should be dealt with the requirement of the problem.

\subsection{Test and Training Lineup} Some lineups should be presented to the MTurk worker so that they can become familiar with the experimental environment before they participate the actual experiment. It is important to setup this properly. The training lineups should be easy and feedback should be provided right after the feedback received. The purpose is to give them an idea how the actual task would look like.

The another way can be to make this training mandatory to participate the experiment. The MTurk worker should have certain proportion of correct responses on these training lineups to allow them to participate. This is often practiced in MTurk task and the workers are very familiar with this approach. In MTurk language it is called the qualification of the worker. Thus to design a MTurk task it is important to set an standard qualification of the worker.

@@

\item {\bf Lineup question:} Each lineup should be presented with a question that the worker has to answer. The question needs to be clear and technical word should be removed as the MTurk workers may not be aware of those terms. The question is important for lineups as well. Very common question to evaluate a lineup is ``Which plot is the most different?". But for complicated studies the question may be quite different \citep{majumder:socio}.

@@

\section{Managing Turk Task}\label{sec:turk_task}

Turk workers are usually small payee workers. There are several issues related to the payment of their effort. These are briefly discussed in the following section.

>>>>

To make sure that the observed data set truly represents the Model \eqref{eqn:turk_model} we suggest three approaches. One is Kolmogorov test statistic approach and the other two approaches are quantiles of $p$-values and closeness of estimated parameters to the true parameters. To illustrate the three approaches we used Model \eqref{eqn:turk_model} as an example but the idea can be extended to any situation. The three approaches are discussed below. \\

{\bf Kolmogorov test statistic approach:} In this approach we simulate 1000 data sets from Model \eqref{eqn:turk_model}  and obtain Kolmogorov test statistic for each set of data as below. $$D_n=\sup_x |F_n(x)-F(x)|$$ where $F_n(x)=\frac1n \sum_{i=1}^n I_{X_i\le x}$ be the empirical distribution function of fitted residuals, $I_{X_i\le x}$ be the indicator function equal to 1 if $X_i\le x$ and equal to 0 otherwise and $F(x)$ be the cumulative function of normal with mean zero(0) and variance $\sigma^2$. We keep the data set that has minimum value for Kolmogorov test statistic since for this data set $F_n(x)$ should be the closest to the desired normal model.  \\

@@

{\bf Closeness of estimated parameters:} When we simulate a data set from the Model \eqref{eqn:turk_model} and fit the model to the data set again, we do not get the parameters estimates same as what we fixed while simulation. For example, we obtained a parameter estimates of 0.5 for true $\beta=3$. We want a data set where the parameter is closed to our fixed slope $\beta=3$.  In this approach we generate 1000 data sets and pick the data set that shows most close estimates of parameters compared to true parameter values. We do this three times to obtain three replications of the data.

@@

\subsection{Sample size estimation} For any experiment it is important to determine the sample size. It is not only related to time and cost of the experiment but also the validity of the results depends on it. In simulation experiment with lineup the sample size means the number of evaluations per lineup. It is different than the number of people who evaluates lineup. If multiple lineups are evaluated by a person, sample size will be larger than number of people recruited from MTurk. For example, if a lineup needs to be evaluated 20 times, we need at least 20 persons since each person does not see the same lineup more than once. This will also enable us to get 10 lineups evaluated if all of these 20 people evaluate 10 lineups each. But all the lineups don't require same number of evaluations. For easy or difficult lineups fewer evaluations are needed.

One approach to assess number of evaluations that are required for a lineup is to have a prior idea of proportion correct for the that lineup. For a given proportion $p$ we want to have margin of error (ME) to be 0.1. Thus we have $$ME =1.96 \sqrt{ \frac 1 n p(1-p)} \le 0.05$$ which gives us the estimation of minimum sample size $$n \geq \frac{p(1-p)}{(0.05/1.96)^2}.$$

If we do not have any prior idea of proportion of correct or power, we may rely on the power of a similar conventional test if available. This can be assumed to be the power or proportion correct for that lineup. Other ways of having an estimate of sample size can be very specific to the problem of interest and should be dealt with the requirement of the problem.

\subsection{Test and Training Lineup} Some lineups should be presented to the MTurk worker so that they can become familiar with the experimental environment before they participate the actual experiment. It is important to setup this properly. The training lineups should be easy and feedback should be provided right after the response is received. The purpose is to give them an idea how the actual task would look like.

The another option is to make this training mandatory to participate the experiment. The MTurk worker should have certain proportion of correct responses on these training lineups to allow them to participate. This is often practiced in MTurk task and the workers are very familiar with this approach. In MTurk language it is called the qualification of the worker. Thus to design a MTurk task it is important to fix a standard qualification of the worker.

@@

\item {\bf Lineup question:} Each lineup should be presented with a question that the worker is asked to answer. The question needs to be clear and technical words should be removed as the MTurk workers may not be aware of those terms. The question is important for lineups as well. Very common question to evaluate a lineup is ``Which plot is the most different?". But for complicated studies the question may be quite different \citep{majumder:socio}.

@@

\section{Managing Turk Task}\label{sec:turk_task} \cite{turk} Mechanical Turk website provides various features that are helpful to maintain and organize the task and manage the workers. Creating, posting, accepting or rejecting tasks and processing payment are done from the MTurk system. It is also possible to screen out workers as per need. For example, none will be interested to recruit people who have bad reputation of getting the work done properly. This can be obtained from each worker's previous work history of total number of accepted task out of total number of submitted task. The web application we developed is for presenting lineups in a way required by the experiment design and collecting data. To get people to the web application we need to design a turk task in MTurk system.

%Turk workers are usually small payee workers. There are several issues related to the payment of their effort. These are briefly discussed in the following section.
